`tidyfun`

### 2020-12-10 tidyfun.Rmd
tidyfun has been updated!!

```{r}
library(tidyfun)
library(tidyverse)
```

@@

```{r}
chf_df %>% 
  select(id, day, activity) %>% 
  filter(day == "Monday") %>% 
  ggplot(aes(y = activity)) + 
  geom_spaghetti(alpha = .05)
```

@@

```{r}
chf_df %>% 
  filter(day %in% c("Monday", "Sunday")) %>% 
  ggplot(aes(y = activity, color = gender)) + 
  geom_spaghetti(alpha = .1) + 
  facet_grid(~ day)
```

@@

```{r}
chf_df %>% 
  group_by(gender, day) %>% 
  summarize(mean_act = mean(activity)) %>% 
  mutate(smooth_mean = tfb(mean_act)) %>% 
  filter(day %in% c("Monday", "Sunday")) %>% 
  ggplot(aes(y = smooth_mean, color = gender)) + 
  geom_spaghetti(size = 1.25, alpha = 1) + 
  geom_meatballs(aes(y = mean_act), alpha = .1) + 
  facet_grid(~ day)
```

@@

```{r}
chf_df %>% 
  filter(day %in% c("Monday", "Sunday")) %>% 
  gglasagna(activity)
```

@@

>>>>

```{r}
library(tidyfun)
library(refundr)
library(tidyverse)
```

@@

```{r}
chf_df %>% 
  select(id, day, activity) %>% 
  filter(day == "Mon") %>% 
  ggplot(aes(y = activity)) + 
  geom_spaghetti(alpha = .05)
```

@@

```{r}
chf_df %>% 
  filter(day %in% c("Mon", "Sun")) %>% 
  ggplot(aes(y = activity, color = gender)) + 
  geom_spaghetti(alpha = .1) + 
  facet_grid(gender ~ day)
```

@@

```{r}
chf_df %>% 
  group_by(gender, day) %>% 
  summarize(mean_act = mean(activity)) %>% 
  mutate(smooth_mean = tfb(mean_act)) %>% 
  filter(day %in% c("Mon", "Sun")) %>% 
  ggplot(aes(y = smooth_mean, color = gender)) + 
  geom_spaghetti(size = 1.25, alpha = 1) + 
  geom_meatballs(aes(y = mean_act), alpha = .1) + 
  facet_grid(~ day)
```

@@

```{r}
chf_df %>% 
  filter(day %in% c("Mon", "Sun")) %>% 
  gglasagna(activity)
```

@@

## Some FPCA

```{r}
# irregular data 
data(dti_df)
dti_fpca = rfr_fpca(Y = "cca", data = dti_df)

dti_df %>% 
  modelr::add_predictions(dti_fpca, var = "cca_fits") %>% 
  filter(case == "control") %>% 
  ggplot(aes(y = cca_fits)) + 
  geom_spaghetti(alpha = .4) + 
  geom_spaghetti(aes(y = cca), color = "blue", alpha = .3) + 
  facet_grid(~sex)
```
